\documentclass[]{letter}

\newcommand{\AH}[1]{%
  $\langle\langle$#1$\rangle\rangle$}%

\newcounter{reviewer}
\newcounter{commentno}[reviewer]

\newcommand{\REVIEW}[2]{
\stepcounter{commentno}
\begin{description}
\item{COMMENT~\thereviewer-\thecommentno: }
#1%
\item{ANSWER~\thereviewer-\thecommentno: }
#2%
\end{description}
\vspace{3mm}
}

\begin{document}

{\bf\huge Title: Overhead of Using Spare Nodes}

{\bf Authors: Atsushi Hori (Riken), Kazumi Yoshinaga (eF-4), Thomas Herault
(UT/ICL), Aur\'elien Bouteiller (UT/ICL), George Bosilca (UT/ICL),
Yutaka Ishikawa (Riken)}

We thank the reviewers for their insightful comments.  We fixed all
the writing issues. The major changed parts in the manuscript are
colored blue. Below are clarifications for some of the questions
asked.

\begin{description}
\stepcounter{reviewer}
\item{Reviewer 1}

\REVIEW{Some of the details in the simulation and evaluation sections are
missing. Was a specific simulator used and, if so, which one? Did the
evaluation use microbenchmarks, if so, which ones? }
{We developed the simulator and the benchmark programs by ourselves. }

\REVIEW{There are a few English language errors in the text. }
{We carefully read the whole manuscript and corrected them.}

\REVIEW{The Related Work section seems to be short. 
The Shadow Replication work by Rami Melhem et al. and ULFM
could be added to this section.}
{We added a paragraph to discuss on the shadow replication in the
  Related Work section.
}

\REVIEW{The impact of communication avoiding
algorithms, which stencil codes are often targeted for, could be
discussed. }
{We also added a paragraph discussing the shadow replication and ULFM in the
  Related Work section. 
}

\stepcounter{reviewer}
\item{Reviewer 2}

\REVIEW{Page 7, Line 30: %
The authors say that the number of combinations of failed node is
the factorial of the number of failed nodes aka. NC(F) = F! , this
subsumes the ordering of node-failures, but the experimental setup
(simulation or evaluation) do not appear to be taking this into
consideration. }
{
This is not true. In out simulations and evaluations, a node failure
happens at a time. To clarify this, we added the procedure at the
beginning of the Simulation section.
}

\REVIEW{Page 3, Line 12: %
The authors do not, benchmark the proposals made for handling the
node failure against the existing fault tolerant framework.}
{
The Tofu network used on the K computer has a fault tolerant
capability (see ``Tofu: A 6D Mesh/Torus Interconnect for Exascale
Computers'',  IEEE Computer, vol.42, ser.11). Yes, we agree with you
that we should have evaluated communication latencies in the presence
of real
node failures. Our focus is the communication behavior with the presence
of faulty node(s) on the large-scale supercomputers. Such 
supercomputers are in operation and it is not allowed for us to have
(artificially generated) faulty node(s) since this affects the other
users. So we decided to benchmark with simulated fault nodes.
}

\REVIEW{The functional demerits of GVR, ULFM were not mentioned other than
not being user friendly}
{
We are sorry if you have such impression from the manuscript. It is not
our intention to claim they are not friendly and we checked the
sentences not to give readers to have such impression.
}

\REVIEW{Have the authors considered Reinit that appeared in IJHPCA last year
that makes Link for: New ULFM API’s user friendly.}
{
We added some explanation on this.
}

\REVIEW{Page 7, Line 37: %
The authors need to specify the basis of the choices they they make
for the simulation setup.

– For example they choose 100x100,12x12x12 and 24x24x24 are there any
implicit basis for these choices like  simulation time.
}
{
100, square of 100 is 10,000, was chosen just because it is a nice
round number to start. 12 is another nice round number for the Tofu
network on the K computer. A Tofu unit consists of 12 nodes and the
nodes in the same Tofu unit are reachable with 1-3 hop(s). The nice
round number on BG/Q is the power of 2. There is no such round number
on TSUBAME2.5 since it has fat-tree network topology. The K computer is
larger than the JUQUEEN (BG/Q) and Tsubame 2.5 and we could benchmark
up to 24x24x24 (13,824) nodes on the K computer. So, we chose 12 as the
base of node numbers. We added the explanation of Tofu unit to the
manuscript.  
}

\REVIEW{Page 4, Line 52: %
The definition of 2D(2,1) is clear and intuitive, but its not so for 3D(2,1).
How does the SNA differ for 3D(2,1) and 2D(2,1)? %
What is the definition for 3D(2,1) spare node allocation?}
{
We added the following description; ``On a 3D network, a job is generally
allocated on a cube. Here, {\it 3D(2,*)} means two 2D side planes
out of 3 dimensions of the cube are allocated as spare nodes. ``
}

\REVIEW{Page 9, Line 13:
– Having a explicit/concrete expression for slowdown ratio would
benefit the reader}
{
The following formula is added.
\[
R^i = L_{no\_sub} / L_{sub}^i
\]
Here, $L_{sub}^i$ is the measured communication latency after
$i$th substitution, $L_{no\_sub}$ is the latency without having any
node failure but having spare node set, and the $R^i$ is the
slowdown ratio at that time.
}

\REVIEW{Page 11, Line 55: %
– What does it mean to have a 3D-sliding for a SNA == 2D(2,1)
}
{
We are very sorry, this is a typo. the SNA should be 3D(2,1) and we
corrected this.
}

\REVIEW{Page 12, Line 9: %
In the discussion section (quite late), the authors mention that a
Figure 3, that appears very early in the paper the spare node \% are for
individual jobs and not for multi
job environment, this would not have
been misleading if mentioned early}
{
We modified some sentences so that Figure 3 is for a single job.
}

\REVIEW{If component failures are common events are we still relying on
redundancy (spare-nodes) to tolerate hardware faults, clear
description of the migration sequence would be helpful. }
{
For this purpose, we added migration action in the assumed scenario of
the proposed substitution in the Introduction section.
}

\REVIEW{The paper has considerable number of Typos and repeated words, there
were more than one instance where  the figures and the corresponding
texts describing them were not matching. }
{
We are dreadfully sorry for these. We checked whole manuscript and
corrected all of them.
}

\REVIEW{– Some of the markings in the Legends in the Figures were not clear,
the use of color in the legend would be  bene cial for the reader}
{
We added colors on the legends.
}

\REVIEW{– English and writing style needs review as The article would benefit
from a close editing. 
– We found it difficult to follow a few of the author’s argument due to
the many stylistic and grammatical errors and grammatical errors. }
{
We are dreadfully sorry for these. We checked whole manuscript and
corrected all of them.
}

\REVIEW{– The ``s<Nq'' is a typo, this should be ``s<Nq''}
{
We corrected this typo.
}

\REVIEW{– The authors quote “white boxes” to be present in the  Figure 6, which
is not explicit.}
{
We added this white box ecplanation.
}

\stepcounter{reviewer}
\item{Reviewer 3}

\REVIEW{There are several ways in which this paper could be
improved. The 5P stencil benchmark is not really described in any
detail, and all simulation and actual performance results are shown in
relative terms. 

The paper could be improved by providing some more
details of the benchmark, including important characteristics such as
message size and message rate. Baseline results that show how the
performance is impacted by suboptimal allocation patterns would be
interesting as well. 
}
{
We added the explanation of the simulation and benchmark programs we
used. 
}

\REVIEW{Since this work is most relevant for very
large-scale jobs, a baseline analysis of actual performance
degradation for different rank mappings would help set bounds for what
the performance implications are. Details on the benchmark would help
improve the ability of the benchmark to simulate actual
applications. }
{
The performance degradation due to the failed node substitution
depends on the communication pattern (P2P, bcast, ...) and how much
time spent on communication (and/or computation). Yes, it is possible
to show some real application performance numbers, however, it is
impossible to show all cases. In theory, the spare node substitution
affects only on communication. If readers know the ratio of
communication time and execution time then the readers can easily
estimate the performance degradation introduced by the substitution.

In addition to the communication pattern of an application, there are
so many parameters, network topology, the number of RDMA engines, and 
how (MPI) communication library is tuned for the network, which can
affect the degradation. We agree it is nice to have upper and/lower bound(s) of
performance differences, this is left for our future work.
}

\REVIEW{There are several working and grammatical errors that
detract from the readability of the paper. It needs a through editing
pass before publication. }
{
We dreadfully sorry for this. We checked whole manuscript to correct
all errors.
}

\end{description}

\end{document}
